\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-22 manuscript/main.tex
modified:   analysis/final_analysis.do 	new file:   figures/plotting_parallel_trend.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	modified:   result_tables/entry_effect_hetero.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/heter_platform_did.tex 	modified:   result_tables/robust_hhi.tex 	modified:   result_

\begin{equation}
    Y_{it} = \rho Y_{it-1} + \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

@@

The result presented in the table \ref{tab:entry_effect} examines the effect of Lianjia's offline stores' entry into an area on various outcomes. Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, suggesting that anticipation of the Lianjia's entry does not affect these metrics. In addition, there is a significant 4\% increase in revenue after the Lianjia's entry ($entry$), suggesting a substantial increase in Lianjia sales. However, the effect on price concessions and number of showings remains statistically insignificant, suggesting that Lianjia's entry does not lead to significant changes in pricing strategies or the number of showings brought to the area.

In the post-entry periods ($post_1$, $post_2$, and $post_3$), the results exhibit notable variations. The first period after entry ($post_1$) shows no significant changes in any of the metrics analyzed. However, in the subsequent post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and the number of house tours. These declines suggest a deterioration in Lianjia's performance and customer engagement, likely attributable to the impact of the epidemic, which led to a decrease in overall revenue. Interestingly, Lianjia's entry does not have a significant effect on price concessions but does show a negative impact on the number of house tours during the epidemic periods. This negative effect is also attributed to the epidemic, which reduced the frequency of house tours due to heightened health concerns and mobility restrictions.

In summary, the entry of a Lianjia into an area significantly boosts its sales initially, without altering its pricing strategies or viewer engagement significantly. However, the positive impact is short-lived, turning negative in subsequent periods, likely exacerbated by external factors like an epidemic.

To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups. The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the entry effect is more pronounced in the high HHI group, with an impact of 6.8\%, and this effect persists into the subsequent period, increasing to 7.8\%. However, following the epidemic, the effect becomes significantly negative in the low HHI group, suggesting that the entry effect is more adversely affected by epidemic policies in less concentrated markets. Conversely, the effect remains non-significant in the high HHI group. Additionally, Lianjia's entry does not significantly influence price concessions in either group, nor does it significantly affect the number of house tours. However, post-epidemic, the number of house tours shows a significantly negative effect in the low HHI group, indicating a more substantial decline in customer engagement in less concentrated markets.

@@

To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period. During our study period, Lianjia implemented the ACN strategy. ACN means to subdivide the whole process of buying and selling a house into different parts, and each part is taken charge of by a person or a store. For this purpose, Lianjia can cooperate with other competitors in the market and integrate their resources to provide a better service to the customers. This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market. In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration. To empirically measure the effect of platformization to the offline stores' operations, we first counted the number of all non-Lianjia stores on the Lianjia's Beke platform within a radius of 410 meters, which allowed us to generate a dummy variable $Treatment_{it}$ to represent whether or not there are any other affiliate stores within the platform in this neighborhood. To dynamically capture the varying effects, we generate $Treatmetn_{it} * year$ by producting the year dummy variable with the $Treatment_{it}$ and include them in our regression model. Since the ACN network was officially established at the end of 2018, we can generate a dummy variable equal to 1 if the year is greater than 2018. We then consider the following regression model:

\begin{equation}
    Y_{it}  = \beta_0 + \sum_{i=-2}^3 Treatment_{it} * year + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
\end{equation}

We treat the year 2016 as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}.

@@

The empirical findings elucidate that prior toz the establishment of the ACN, there is an absence of discernible effects attributable to anticipation. Subsequent results for the fiscal year 2018 reveal that the ACN exerts a considerable influence on revenue generation, yet it manifests no significant impact on the metrics of price concessions and the number of house tours. This phenomenon indicates that the efficacy of the ACN model does not derive from an augmentation in client base through absorption but rather through the synthesis and integration of comprehensive data on the supply side. Post-2018 observations indicate the maturation of the platformization process, evidencing its expanding influence from the supply to the demand sector. Notably, a marked negative effect on price concessions is observed, underscoring the ACN's significant role in influencing consumer decision-making processes.

However, the years 2021 and 2022 witnessed a mitigated advantage of these factors due to the global epidemic, underscoring an imperative insight; despite the foundational establishment of online platformization, the inherent benefits of physical storefronts remain irreplaceable. This realization requires a re-evaluation of economic models, advocating a harmonious co-evolution of online and offline market paradigms. This strategic integration aims to leverage the unique strengths of each model to foster a more resilient and adaptive economic ecosystem.

To check the robustness of the result, we also calculated the average number of watching times in the beke's website during the sample periods and estimated the model separately (need to further refine and reformulate).

>>>>

\begin{equation}
    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

@@

The results presented in the table \ref{tab:entry_effect} analyze the impact of Lianjia's offline stores entering segmented markets. Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that anticipation of Lianjia's entry does not influence these metrics. Post-entry ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales. However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period. Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.\% increase in the first post-entry period. Nonetheless, this effect lessens in $post_2$, though it remains significant in $post_3$. This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.

In terms of the transaction period, the offline store's influence is always not significant, which suggests that the offline store's entry does not help to match the buyers and sellers in searching the houses, which is in line with the intuition that when platform is more mature, people's searching behavior is more likely to be online. Lastly, regarding price concessions, the entry of Lianjia's offline stores exhibits a 4.5\% positive effect. This suggests that the presence of offline stores may facilitate an increase in price concessions. This effect can be attributed to the enhanced efficiency in matching buyers with suitable properties, thereby encouraging sellers to be more amenable to price negotiations. Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.

In summary, the entry of Lianjia into a segmented market initially results in a significant increase in revenue and facilitates a higher number of house tours, which, in turn, leads to greater price concessions. However, this positive impact is transient, diminishing over time due to increased market competition and external factors such as the COVID-19 pandemic. This suggests that while Lianjia's entry provides a short-term boost to its market performance, the sustainability of this effect is challenged by both competitive dynamics and unforeseen external shocks.

To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups. The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the income effect for Lianjia remains consistent across both groups. Specifically, income increases by 9.2\% during the entry period, with the effect decreasing to 5.1\% in the subsequent period for the higher HHI group, and increasing by 9.6\% during the entry period and decreasing to 4.7\% for the lower HHI group. However, a significant difference emerges in the number of house tours. The entry of Lianjia increases the number of house tours by 2.9\% for the higher HHI group and by 4.4\% for the lower HHI group. In the subsequent period, the effect diminishes for the lower HHI group, indicating that the entry of new competitors mitigates Lianjia's entry effect. Conversely, the entry effect remains significant for the higher HHI group. This analysis underscores the varying impacts of market concentration on Lianjia's market performance post-entry.

Furthermore, in columns 5 and 6, the entry of Lianjia's offline stores significantly shortens the transaction period for the higher HHI group. This suggests that offline stores enhance market efficiency by better matching buyers and sellers. Conversely, this effect is not significant in the lower HHI group, indicating that the benefits of offline stores diminish in more competitive markets. Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the lower HHI group initially. However, by the $post_3$ period, the effect becomes significant and positive. This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market. [ THERE IS ALSO A GRAPH OF PARALLEL TREND NEED TO BE ADDED HERE. ]

@@

To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period: Lianjia's implementation of a downstream consolidation strategy. This strategy involves the integration of offline stores with online platforms, leveraging the advantages of Lianjia's Agent Cooperation Network (ACN) strategy. The ACN strategy subdivides the entire process of buying and selling a house into distinct parts, with each part managed by a specific agent or store. By sharing transaction dividends among multiple stores, Lianjia fosters cooperation with other market competitors and integrates their resources to enhance service quality for customers. This approach is designed to improve efficiency and customer satisfaction by combining online and offline resources, thus providing a comprehensive and streamlined service experience.

This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market. In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration. To empirically measure the effect of platformization to the offline stores' operations, we first counted the number of all non-Lianjia stores on the Lianjia's Beke platform within a radius of 410 meters, which allowed us to generate a dummy variable $Treatment_{it}$ to represent whether or not there are any other affiliate stores within the platform in this neighborhood. To dynamically capture the varying effects, we generate $Treatmetn_{it} * year$ by producting the year dummy variable with the $Treatment_{it}$ and include them in our regression model. Since the ACN network was officially established at the end of 2018, we can generate a dummy variable equal to 1 if the year is greater than 2018. We then consider the following regression model:

\begin{equation}
    Y_{it}  = \beta_0 + \sum_{i=1}^5 Treatment_{it} * year + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
\end{equation}

By focusing on 2017 as the baseline, we can empirically estimate the outcomes with greater precision and reliability, ensuring that our analysis accurately reflects the impact of Lianjia's strategy without the confounding effects of prior periods. Other settings are consistent with previous table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.

@@

The empirical findings indicate that during the first year of consolidation, Lianjia's transaction revenue did not show a statistically significant difference from zero. However, from 2019 to 2021, the transaction revenue demonstrated a significant positive increase, ranging from 4.9\% to 2.6\%. Additionally, the consolidation of the platform had a significantly positive impact on the number of house tours, which increased by 3.9\% to 6.4\% from 2018 to 2022, with this trend continuing upward throughout the sample period. Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the data clearly show that the platformization effect is substantially more pronounced. This suggests that the platformization strategy is markedly more effective than the offline store entry strategy in generating revenue and attracting buyers in the market. These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion.

However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers. A similar pattern is observed in price concessions, suggesting that the platformization strategy does not contribute to reducing price concessions. While the platformization strategy is less effective in influencing individuals' decision-making processes compared to offline store entry, it proves more effective in increasing revenue and the number of house tours. This discrepancy highlights that the platformization strategy excels in attracting customers and generating revenue, but falls short in aiding the matching and negotiation process. These findings align with the intuition that platformization is more likely to draw customers and boost revenue, yet it is less effective in assisting buyers and sellers in reaching agreements.

To further investigate the impact of market concentration on the effectiveness of the platformization strategy, we classified the samples into high and low Herfindahl-Hirschman Index (HHI) groups and estimated the model separately for each group. The high HHI group, representing markets with higher concentration, revealed that the platformization strategy does not confer significant benefits for Lianjia's operations. Conversely, in the low HHI group, indicative of less competitive markets, the platformization strategy significantly increases revenue. This suggests that the platformization strategy is more effective in less competitive markets, enhancing Lianjia's competitiveness. In terms of the number of house tours, the effect of platformization is consistent across both high and low HHI groups. This consistency aligns with the intuition that consumer preferences for different types of brokerages are similar, and individuals are equally likely to search for houses online regardless of the brokerage's market share. Moreover, our analysis in columns 5 to 8 shows that the platformization strategy does not have a significant effect on the transaction period or price concessions. This finding suggests that the platformization strategy does not facilitate better matching between buyers and sellers or improve the negotiation process. This aligns with the intuition that while the platformization strategy can attract more customers and generate revenue, it does not inherently improve the efficiency of matching buyers and sellers or negotiating terms because most of the transactions are still offline based.
